Self-supervised representations promise robustness to nuisance variation; whether
that robustness transfers across novel nuisance families is rarely tested. We
probe this on a leakage-controlled HAM10000 longitudinal proxy with three
disjoint synthetic nuisance families --- partitioned along the deterministic-
augmentation axis --- training a JEPA-style latent predictor on stable pairs
from two of three families and evaluating on the third unseen family. We report
a preliminary nine-experiment arc. Across four frozen-natural-image
configurations spanning two pretraining paradigms within the ViT-B
class (DINOv2 ViT-B/14, OpenAI CLIP ViT-B/16), two predictor
scaffolds (linear with identity warm-start, 2-layer identity-residual
MLP), and two optimisers (SGD, Adam), test $\auroc$ on the held-out
family lands in $0.25$--$0.29$ --- below random and below the
strongest oriented baseline (pixel L2 at $0.580$). A frozen general-medical
backbone (BiomedCLIP, PMC-15M scientific-article figures, with no
documented raw HAM10000/ISIC archive ingestion) lifts test $\auroc$ by
only $+0.04$ to $0.329 \pm 0.012$ across $5$ seeds. A frozen
dermoscopy-pretrained backbone
(DermLIP, Derm1M) lifts test $\auroc$ to $\mathbf{0.944 \pm 0.003}$ across $5$
seeds, $+0.363$ above the strongest baseline and the only above-random result on
the held-out third family across the six runs that evaluate on it
(EXP-004 through EXP-008). Holding architecture (ViT-B/16) and
predictor (linear) constant, varying only the pretraining-data domain
produces a $+0.66$ end-to-end $\auroc$ swing (web $\to$ dermoscopy)
that is concentrated in the dermoscopy-specific step ($+0.62$ of $+0.66$,
with the residual $+0.04$ at the web $\to$ general-medical step).
\textbf{We explicitly do not claim that this swing is dermoscopy-domain
transfer}: DermLIP's Derm1M corpus does not list HAM10000 as a source, but a
perceptual-hash audit confirms HAM10000 images leaked into it via reproduced
figures in its scraped literature, so image-level overlap is established (at
small, lower-bounded scale), and the experiments reported here cannot separate
dermoscopy-domain transfer from such overlap. We release the methodology, the configurations,
and the run archive, and sketch a candidate partition experiment (a
non-HAM10000 dermoscopy SSL pretrain) as a natural next step we may
consider after gathering community feedback on the methodology and the
preliminary results. The contribution is the
proxy-task design, the failure characterisation, and a clearly scoped open
question --- not a conclusion about whether frozen-backbone JEPA generalises on
dermoscopy.
