\section{Introduction}
\label{sec:introduction}

Lesion monitoring is fundamentally a change-detection problem under heavy
nuisance variation. Repeated photographs of the same skin lesion vary because
of illumination, framing, hair occlusion, camera optics, and compression;
clinically meaningful change is small relative to that nuisance envelope.
Self-supervised learning (SSL) representations are routinely pitched as
broadly transferable across image distributions and tasks
\citep{caron2021dino, oquab2024dinov2, radford2021clip} --- a property
we read as approximate invariance to many of the
photometric and framing nuisances we care about here. The
joint-embedding predictive architecture (JEPA) family
\citep{lecun2022path, assran2023ijepa} explicitly frames prediction in
representation space as the path to invariance. Our question is narrow:
\emph{when a JEPA-style latent predictor over a frozen vision backbone is
trained on stable-pair invariance with respect to one set of synthetic nuisance
operations, does that invariance generalise to a disjoint nuisance family the
predictor never saw at training time?}

We probe this on HAM10000 \citep{tschandl2018ham10000}. HAM10000 is
cross-sectional, so we construct a leakage-controlled longitudinal proxy:
lesion-ID-aware splits, synthetic stable-pair augmentations applied
post-split, and changing-pair construction matched on diagnosis and anatomical
site. Three deterministic synthetic nuisance families --- \strongfam,
\strongholdone, and \strongholdtwo\ --- are designed to share no operation
type with each other. We train on stable pairs drawn from $\{\strongfam,
\strongholdone\}$ and evaluate on a third unseen family $\strongholdtwo$. The
predictor is a small function $g_\theta : \mathbb{R}^d \to \mathbb{R}^d$ over
the L2-normalised output of a frozen backbone --- linear with identity
warm-start, or a 2-layer identity-residual MLP --- trained to minimise L2-MSE
between predicted and observed target latents on stable pairs. Across nine
experiments we vary predictor class, optimiser, and backbone independently
while holding every other knob constant.

\textbf{This paper is a preliminary report.} The single positive result we
observe (frozen DermLIP at $0.944 \pm 0.003$ test $\auroc$ across $5$ seeds)
\emph{cannot be attributed to dermoscopy-domain transfer with the experiments
reported here.} DermLIP's pretraining corpus, Derm1M
\citep{yan2025derm1m}, almost certainly contains HAM10000 raw images, and the
BiomedCLIP partition we report rules out only the narrower
``PMC-15M-style biomedical-figure pretraining (with PMC-15M's
undocumented dermatology fraction) is sufficient'' alternative; it
does not preclude other medical pretraining corpora with substantial
dermatology content. A natural follow-up experiment
we sketch as EXP-009 (a self-pretrained DINOv2 on a non-HAM10000
dermoscopy corpus, \S\ref{sec:followup}) would aim to close the
partition; we deliberately publish at this stage --- before committing
to that build --- to gather community feedback on the methodology and
the partition design.

Figure~\ref{fig:cross-backbone-gradient} previews the headline. Test $\auroc$
on $\strongholdtwo$ is below random for every frozen natural-image
configuration we ran (four cells spanning two backbones, two predictor
scaffolds, and two optimisers); barely lifts under a frozen general-
medical backbone (BiomedCLIP, $0.329 \pm 0.012$); and reaches
$0.944 \pm 0.003$ under a frozen dermoscopy-specific backbone (DermLIP),
with the contamination caveat marked on the right.

\paragraph{Contributions.}
\begin{itemize}
\item \textbf{Methodological.} A leakage-controlled HAM10000 longitudinal-proxy
      task with three disjoint synthetic nuisance families and a
      \texttt{train-on-two/evaluate-on-third} protocol, released as code,
      configurations, and reproduction launchers.
\item \textbf{Empirical (negative).} Across four frozen-natural-image
      configurations (DINOv2 / CLIP $\times$ linear / MLP $\times$ SGD
      / Adam, with the four cells listed in
      Appendix~\ref{app:per-run}), test $\auroc$ on the held-out third
      family inverts below random.
\item \textbf{Empirical (positive but unpartitioned).} Frozen DermLIP reaches
      test $\auroc = 0.944 \pm 0.003$ across $5$ seeds, $+0.363$ above the
      strongest baseline. The win cannot yet be attributed to dermoscopy-
      domain transfer rather than HAM10000 image-level overlap;
      EXP-009 (\S\ref{sec:followup}) would be one way to close the
      partition.
\item \textbf{Empirical (negative-as-partition).} Frozen BiomedCLIP ---
      a biomedical-figure-pretrained backbone with no documented raw
      HAM10000/ISIC archive ingestion, and with an undocumented but
      plausibly small dermatology fraction --- lifts only $+0.04$ over
      web CLIP, narrowing the open question to dermoscopy-rich
      pretraining.
\item \textbf{Reproducibility.} Every primary-tier run is archived publicly at
      \runarchive\ with manifests, embeddings, metrics, model card, and logs.
      A single launcher script reproduces each run end-to-end on a free A10G
      via Hugging Face Jobs.
\item \textbf{A clearly scoped open question.} A candidate partition
      experiment (EXP-009) and the decision table that would attach to
      it are stated up front (\S\ref{sec:followup}) rather than treated
      as future work in passing.
\end{itemize}
