\section{Experimental setup}
\label{sec:experimental-setup}

\paragraph{Backbones.} Five frozen vision backbones cover the
architectural and pretraining-data axes the paper varies
(Table~\ref{tab:backbones}).

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}llrlp{0.36\linewidth}@{}}
\toprule
Backbone & Arch. & $d$ & Pretraining & Hugging Face Hub path \\
\midrule
DINOv2 ViT-S/14      & ViT-S/14 & $384$ & LVD-142M (web)   & \path{facebook/dinov2-small} \\
DINOv2 ViT-B/14      & ViT-B/14 & $768$ & LVD-142M (web)   & \path{facebook/dinov2-base} \\
OpenAI CLIP ViT-B/16 & ViT-B/16 & $512$ & WIT (web)        & \path{openai/clip-vit-base-patch16} \\
DermLIP ViT-B/16     & ViT-B/16 & $512$ & Derm1M (derm.)   & \path{redlessone/DermLIP_ViT-B-16} \\
BiomedCLIP ViT-B/16  & ViT-B/16 & $512$ & PMC-15M (med.)   & \path{microsoft/BiomedCLIP-PubMedBERT_256-vit_base_patch16_224} \\
\bottomrule
\end{tabular}
\caption{Frozen vision backbones evaluated. Citations: DINOv2
\citep{oquab2024dinov2}, OpenAI CLIP \citep{radford2021clip}, DermLIP
\citep{yan2025derm1m}, BiomedCLIP \citep{zhang2023biomedclip}. Hugging Face (HF) Hub
paths resolve at \url{https://huggingface.co/}\,$\langle$path$\rangle$.}
\label{tab:backbones}
\end{table}

\paragraph{Training.}
$200$ epochs at batch size $128$ on $1{,}000$ training pairs. The linear
predictor uses SGD at LR $3\!\times\!10^{-2}$ with weight decay $10^{-3}$
applied to \texttt{(weight $-$ I)}. The MLP predictor uses Adam at LR
$10^{-3}$ with decoupled weight decay $10^{-4}$. Identity warm-start in both
cases.

\paragraph{Compute.}
Each primary-tier run executes on a single NVIDIA A10G 24~GB via Hugging Face
Jobs in approximately $95$--$100$ minutes wall-clock end-to-end (manifest build,
embedding export, baseline evaluation, predictor training, and run-archive
upload). Hosted dependency versions are pinned in
\texttt{scripts/hf\_jobs\_constraints.txt}.

\paragraph{Code, configurations, and run archive.}
Source code is at
\url{https://github.com/AbdelStark/derma-jepa}.
Per-experiment configurations and launchers live under
\texttt{configs/data/} and \texttt{scripts/}, one pair per experiment. The
run archive containing every primary-tier run's manifests, embeddings,
metrics, model card, and logs is at \runarchive.
