\section{Limitations}
\label{sec:limitations}

\begin{enumerate}[leftmargin=2em]
\item \textbf{Pretraining contamination is unpartitioned.} The DermLIP
      positive cannot be attributed to dermoscopy-domain transfer with
      the experiments reported here. EXP-009 (\S\ref{sec:followup}) is
      one candidate partition experiment we have sketched; until such
      a partition is run, the headline should be read as ``frozen
      DermLIP plus a linear scaffold reaches $\auroc = 0.944$ under
      the conditions of \S\ref{sec:method}, with HAM10000 contamination
      unpartitioned'' rather than as a transfer claim.
\item \textbf{Synthetic nuisance.} The three families are deterministic
      operations on PIL images. Real-world dermoscopic acquisition
      variability is more complex; the proxy is methodological and is
      identified as such.
\item \textbf{Single-architecture-class comparison.} All four backbones
      in the cross-backbone gradient are ViT-B-class (CLIP architecture
      at patch size $16$ for OpenAI CLIP, DermLIP, and BiomedCLIP;
      DINOv2 architecture at patch size $14$ for DINOv2). Other
      architecture classes --- different capacity tiers, SigLIP,
      hierarchical or convolutional backbones --- are unprobed. Future
      work should vary architecture class as a separate axis.
\item \textbf{Single dataset.} HAM10000 is the only evaluation corpus.
      ISIC archive components and PAD-UFES-20 are unprobed in this work
      and are candidates for v2 experiments and for the EXP-009 corpus.
\item \textbf{HAM10000 is cross-sectional.} The dataset has no real
      same-lesion-over-time pairs; the longitudinal proxy is synthetic
      throughout. Validating the methodology on a real longitudinal
      dataset (e.g.\ ISIC 2020's serial-imaging metadata) is an explicit
      next-stage follow-up.
\item \textbf{Single scaffold class on the dermoscopy backbone.} The MLP
      ablation (EXP-005, EXP-006a) was run only on DINOv2; an MLP-on-DermLIP
      run was not performed. Predicted to land at or above EXP-007's $0.944$
      since the linear scaffold already saturates training, but unverified.
\end{enumerate}
