\section{Nuisance-family operation specifications}
\label{app:nuisance-operations}

The three nuisance families in \S\ref{sec:method:nuisance} are
implemented in \path{src/derma_jepa/public_data.py}: \strongfam\ at
line 751 (\path{_apply_strong_nuisance}), \strongholdone\ at line 829
(\path{_apply_strong_held_out_nuisance}), and \strongholdtwo\ at line
494 (\path{_apply_strong_held_out_2_nuisance}). Each function takes a
PIL image, a per-pair index, and a NumPy \texttt{Generator}, applies
the operations below in the listed order, and returns the
nuisance-perturbed image alongside a recipe dictionary recording the
sampled parameter values.

\subsection*{\strongfam}
Photometric, geometric, and sensor-noise perturbations that model
ordinary acquisition variability.
\begin{itemize}
\item Brightness, contrast, and saturation jitter applied independently:
      each scaled by $u \sim \mathrm{Uniform}(0.6, 1.4)$ via PIL
      \texttt{ImageEnhance}.
\item Affine transform: rotation $\theta \sim \mathrm{Uniform}(-15^{\circ}, 15^{\circ})$,
      isotropic scale $s \sim \mathrm{Uniform}(0.82, 1.00)$, translation
      $(t_{x}, t_{y}) \sim \mathrm{Uniform}(-0.05, 0.05)^{2}$ in image-fraction units.
\item Horizontal flip with probability $0.5$.
\item Gaussian blur with radius $r \sim \mathrm{Uniform}(0.5, 1.5)$\,px.
\item Additive Gaussian noise with $\sigma \sim \mathrm{Uniform}(0, 8)$
      on the $0$--$255$ scale.
\item JPEG round-trip at quality $q \sim \mathrm{Uniform}\{45, \dots, 70\}$.
\end{itemize}

\subsection*{\strongholdone}
Disjoint operation set: HSV colour rotation, posterisation, sharpening,
motion blur, occlusion, and aggressive JPEG compression. No transform
type overlaps with \strongfam.
\begin{itemize}
\item HSV hue rotation by $\Delta h \sim \mathrm{Uniform}(-12^{\circ}, 12^{\circ})$.
\item Posterise to $b \sim \mathrm{Uniform}\{4, 5, 6\}$ bits per channel.
\item Unsharp-mask sharpen with PIL \texttt{ImageFilter.UnsharpMask}
      (radius $2$, percent $\sim \mathrm{Uniform}(120, 200)$, threshold $3$).
\item Motion blur with a linear kernel of length $k \sim \mathrm{Uniform}\{5, \dots, 15\}$\,px,
      orientation chosen uniformly from \{vertical, horizontal\}.
\item Random rectangular erasing covering
      $\alpha \sim \mathrm{Uniform}(0.06, 0.18)$ of the image area, fill
      colour sampled per call from $\{0, 128, 255\}$.
\item JPEG round-trip at quality $q \sim \mathrm{Uniform}\{20, \dots, 40\}$.
\end{itemize}

\subsection*{\strongholdtwo}
Disjoint operation set: gamma, colour-temperature, vignette,
salt-and-pepper noise, and high-quality JPEG. No transform type overlaps
with \strongfam\ or \strongholdone.
\begin{itemize}
\item Gamma correction with $\gamma \sim \mathrm{Uniform}(0.6, 1.6)$
      (non-linear, distinct from contrast).
\item Colour-temperature shift: scale R by
      $T \sim \mathrm{Uniform}(0.85, 1.15)$ and divide B by $T$.
\item Radial vignette with cos$^{2}$ falloff at strength
      $v \sim \mathrm{Uniform}(0.25, 0.55)$ from image centre.
\item Salt-and-pepper impulse noise covering
      $\rho \sim \mathrm{Uniform}(0.005, 0.025)$ of pixels with value
      drawn uniformly from $\{0, 255\}$.
\item JPEG round-trip at quality $q \sim \mathrm{Uniform}\{80, \dots, 95\}$
      (distinct from \strongfam's $45$--$70$ and \strongholdone's $20$--$40$).
\end{itemize}

\paragraph{Disjointness.} The three operation sets share no transform
type --- a property enforced by inspection of the function bodies and
re-checked in the code review for every new family proposed. JPEG
quality ranges are chosen non-overlapping so that the post-pipeline
compression artefact is family-distinguishable. The composite
augmentation pipeline is deterministic in the per-pair seed: the same
seed reproduces byte-identical perturbed images, which is exploited by
the verification harness in \texttt{tests/test\_public\_data\_pipeline.py}.
