\section{Bootstrap CI protocol}
\label{app:bootstrap-protocol}

Every $\auroc$ in the paper is reported with a $1{,}000$-sample
percentile bootstrap $95\%$ confidence interval. The implementation is
at \path{src/derma_jepa/metrics.py:66}
(\path{bootstrap_auroc_ci}); the unit tests at
\path{tests/test_metrics.py} cover the AUROC point estimate, the
bootstrap CI shape, the equal-error-rate threshold, and the
FPR-at-fixed-TPR computation.

\paragraph{Resampling unit.} The resampling unit is the pair: each
bootstrap sample draws $N$ stable--changing pair indices with
replacement from the $N = 2{,}000$ pairs in a split, recomputes
$\auroc$ on the resampled set, and records the value. The $2.5\%$ and
$97.5\%$ percentiles of the $1{,}000$ resampled $\auroc$ values define
the reported CI. Pair-level resampling matches the unit at which the
score $s$ is computed (eq.~\ref{eq:score}); it does not stratify by
diagnosis or by anatomical site.

\paragraph{Determinism.} The bootstrap RNG is seeded from the same
project seed used for split assignment, predictor initialisation, and
pair generation. Re-running a configuration with the same seed
reproduces byte-identical CIs.

\paragraph{Seed-mean CIs.} For the EXP-007 and EXP-008 seed sweeps
(\S\ref{app:per-run:seed-sweep}), the reported $\pm$ values are
unbiased standard deviations across the five seed-mean $\auroc$
estimates; the reported ``$95\%$ CI[mean]'' is the seed-mean point
estimate plus and minus $1.96$ times the seed-mean standard error
($\sigma / \sqrt{n}$ with $n = 5$). These intervals quantify seed
variance and are distinct from the per-pair bootstrap CIs reported on a
single seed.

\paragraph{Companion metrics.} Alongside $\auroc$, every run reports
AUPRC, the equal-error-rate threshold, and the false-positive rate at a
fixed true-positive rate of $0.8$. Each is bootstrapped under the same
protocol. AUPRC tracks $\auroc$ rank-monotonically across the nine runs;
EER and FPR-at-TPR add operating-point information that is sensitive to
the train$\to$test score-distribution shift discussed in
\S\ref{sec:analysis:inversion}. Per-run values are mirrored at
\texttt{<run\_id>/metrics.json} under \runarchive.
