\section{Representation-health checks}
\label{app:representation-health}

Three representation-health diagnostics accompany every run, computed by
\texttt{src/derma\_jepa/training.py:479} (\texttt{\_collapse\_checks}) on
the $L^{2}$-normalised predictor outputs over the test split. The
\texttt{collapsed} flag triggers if either the prediction-norm minimum
or the dimension-variance minimum falls below $10^{-8}$ --- a
representation collapse would render the cosine-distance score
ill-defined. None of the nine primary-tier runs trips the flag.

\paragraph{Prediction-norm mean and minimum.} The mean and minimum
$L^{2}$ norm of the un-normalised predictor outputs across the test
pairs. A close-to-zero minimum would signal a collapsed direction; a
close-to-one mean confirms that L2-normalisation is acting on
non-degenerate vectors. All nine runs report mean $\geq 0.97$ and
minimum $\geq 0.83$.

\paragraph{Dimension-variance mean and minimum.} The mean and minimum
of the per-dimension variances of the predictor output across the test
pairs. A near-zero minimum-variance dimension would signal that the
predictor has effectively dropped a coordinate. All nine runs report a
minimum of order $10^{-3}$ or larger; the natural-image-backbone runs
(EXP-004 / EXP-005 / EXP-006a / EXP-006b) sit one order of magnitude
above the DermLIP and BiomedCLIP runs, consistent with the fit-quality
gap and not with collapse.

\paragraph{Collapse flag.} Binary; $\mathrm{true}$ if either of the two
minima above falls below $10^{-8}$. None of the nine reported runs is
flagged. The threshold is conservative: $10^{-8}$ corresponds to roughly
single-precision noise on a unit-norm vector and is intended to catch
hard collapse rather than soft anisotropy.

\paragraph{Where the values live.} Each run's
\texttt{metrics.json}\,$\to$\,\texttt{representation\_health} block
records the four numerical diagnostics and the binary flag. The
aggregator \texttt{scripts/aggregate\_seed\_sweep.py} pulls these
fields when computing seed-sweep summaries.
