\section{Compute budget}
\label{app:compute-budget}

Every primary-tier run executes on a single NVIDIA A10G 24~GB via
Hugging Face Jobs (\texttt{a10g-large}). The wall-clock breakdown for
the canonical EXP-004 recipe ($\sim$95--100~min end-to-end, measured at
$\sim$$98$~min from the EXP-004 \texttt{progress.jsonl} timestamps) is
approximately:

\begin{itemize}
\item Manifest build, deterministic-augmentation pair generation, and
      data-audit checks: $\sim$10~min.
\item Backbone embedding export over $6{,}000$ pairs ($\times 2$ sides):
      $\sim$10~min for ViT-B/14 and ViT-B/16 backbones.
\item Cheap-baseline evaluation (pixel L2, SSIM, raw cosine): $\sim$5~min.
\item Predictor training ($200$ epochs, batch $128$, $\sim$8 steps per
      epoch): $\sim$50~min for the linear predictor; the MLP predictor
      runs in the same envelope.
\item Bootstrap CIs, representation-health checks, report writing,
      run-archive upload: $\sim$10~min.
\end{itemize}

The MLP-on-DINOv2 runs (EXP-005 and EXP-006a) take $\sim$105~min
because the MLP forward/backward is approximately twice the linear
predictor's. The DermLIP and BiomedCLIP runs sit in the same
$\sim$$95$-minute envelope as the linear DINOv2 and CLIP runs: backbone
forward dominates only the embedding-export phase, and once
embeddings are cached, predictor training is backbone-independent.

\paragraph{Total for the paper.} Nine primary-tier runs at
$\sim$$95$--$105$~min each plus eight additional seed-sweep runs at
$\sim$$95$~min each
totals approximately $28$ A10G-hours of compute, plus an additional
$\sim$3~A10G-hours absorbed by two infrastructure-flake re-launches
during the seed-sweep cohort. All accumulated at Hugging Face Jobs
free-tier rates; the launchers are committed under \path{scripts/}
and the pinned dependency versions for the hosted environment are at
\path{scripts/hf_jobs_constraints.txt}.

\paragraph{Reproducibility cost.} Reproducing the entire nine-run arc
plus the seed sweep from a clean checkout requires the same
$\sim$$28$--$31$ A10G-hours, plus a one-time HAM10000 download (the source manifest
caches it once). No private data, no local GPU.
