\section{Reproducibility checklist}
\label{app:reproducibility-checklist}

The checklist follows the standard NeurIPS / ML reproducibility template,
mapped to specific repository assets.

\begin{enumerate}[leftmargin=2em]
\item \textbf{Code.} Public at
      \href{https://github.com/AbdelStark/derma-jepa}{\texttt{github.com/AbdelStark/derma-jepa}}.
      Pinned dependency manifest at \texttt{pyproject.toml} and
      \texttt{uv.lock}; hosted-environment pins at
      \texttt{scripts/hf\_jobs\_constraints.txt}.
\item \textbf{Data.} HAM10000 \citep{tschandl2018ham10000} via the
      \texttt{abdelstark/ham10000} HF dataset mirror; the source manifest
      and download path live at \texttt{src/derma\_jepa/public\_data.py}.
\item \textbf{Configurations.} One YAML per primary-tier run under
      \texttt{configs/data/}; every run mirrors its exact
      \texttt{config.yaml} alongside \texttt{metrics.json} and
      \texttt{baseline\_metrics.json} at \texttt{<run\_id>/} on the run
      archive (\runarchive).
\item \textbf{Seeds and determinism.} Default seed $20260422$. Seed
      controls split assignment, pair generation, augmentation
      sampling, predictor initialisation, and bootstrap resampling.
\item \textbf{Hardware.} Single NVIDIA A10G 24~GB via Hugging Face Jobs
      (\texttt{a10g-large}). Reproduction cost is $\sim$25 A10G-hours
      for the nine runs plus the seed sweep
      (Appendix~\ref{app:compute-budget}).
\item \textbf{Hyperparameters.} Listed in
      Appendix~\ref{app:hyperparameters}.
\item \textbf{Metrics and uncertainty.} Primary $\auroc$ with $1{,}000$-sample
      pair-level percentile bootstrap $95\%$ CIs; companion AUPRC, EER,
      and FPR-at-fixed-TPR. Implementation:
      \texttt{src/derma\_jepa/metrics.py}; tests:
      \texttt{tests/test\_metrics.py}.
\item \textbf{Numbers.} Every quantitative claim in the paper traces to
      \texttt{paper/figures/locked-numbers.json} and is verified at
      build time by \texttt{paper/verify\_claims.py} against the
      run-archive mirror.
\item \textbf{Negative results and ablations.} The full nine-run
      sequence is reported, including the seven runs whose test $\auroc$
      lands in the $0.25$--$0.33$ band.
\item \textbf{Compute budget.} Reported in
      Appendix~\ref{app:compute-budget}.
\item \textbf{Licence.} Source code under MIT (see \texttt{LICENSE});
      run-archive artefacts inherit the HF dataset licence.
\item \textbf{Intended use.} The methodology and the run archive are
      research artefacts. The paper makes no clinical or diagnostic
      claim; the proxy is synthetic and the contamination caveat is
      explicit (\S\ref{sec:limitations}).
\end{enumerate}
