\section{EXP-009 design (candidate)}
\label{app:exp009-design}

This appendix expands the EXP-009 sketch in \S\ref{sec:followup} into
the operational detail required to evaluate the proposal. We commit
the design --- including the decision table mapping outcome bands to
claim revisions --- in advance so that, should we (or anyone else)
choose to run it, the result cannot be re-interpreted post-hoc. We do
not commit at this stage to running it ourselves; whether to invest the
effort, alter the design, or pursue a different follow-up entirely is a
decision we are deferring until after community feedback on this
preliminary release.

\subsection{Goal}
Self-pretrain a vision encoder on a non-HAM10000 dermoscopy corpus, then
re-run the EXP-004 recipe on top with the linear predictor. The encoder
sees no HAM10000 image during pretraining, so the EXP-007-style positive
on \strongholdtwo\ --- if it appears --- can no longer be attributed to
HAM10000 image-level overlap and must reflect dermoscopy-domain transfer.

\subsection{Pretraining corpus}
Assemble from publicly available dermoscopy / clinical-skin sources, with
provenance audit on every component to confirm HAM10000 exclusion:
\begin{itemize}
\item ISIC archive components other than HAM10000 (BCN20000
      \citep{combalia2019bcn20000}, MSK-1 through MSK-5, UDA, Mednode,
      and similar legacy archives).
\item DermNet NZ public images and DermQuest-derived archival mirrors,
      where surviving (the original DermQuest portal was retired in
      $2019$ and surviving derivative releases would be the actual
      source); clinical, not dermoscopic, included to broaden the
      visual distribution.
\item PAD-UFES-20 and 7-point checklist datasets (each cross-checked
      for HAM10000 overlap by lesion-ID and SHA-256 hash).
\end{itemize}
Provenance audit: every image must carry a source attribution and a
SHA-256 hash. The HAM10000 image-hash set is computed from the source
manifest and excluded by hash; any image whose source attribution is
ambiguous is excluded by default.

\subsection{Pretraining objective}
DINOv2 ViT-B/14 architecture (i.e.\ the same family as the EXP-004
backbone, so any test-$\auroc$ change is attributable to pretraining
data, not architecture), trained for $\sim$20 epochs with a JEPA-style
or masked-image-modelling objective. Hyperparameters target a
$\sim$$200{,}000$-step regime on a $\sim$$8\times$~A10G or
$1\times$~A100 budget. Pretrain-quality is checked by linear-probing on
a held-out HAM10000 split for diagnosis classification --- a sanity
check that the encoder has not overfit to its training distribution.

\subsection{Probe}
After pretraining, the encoder is frozen and the EXP-004 recipe runs on
top: linear predictor with identity warm-start, SGD, weight-decay-on-$(W-I)$,
$200$ epochs, the same lesion-ID splits, the same $1{,}000 + 1{,}000$
pairs per split, the same three-family augmentation pipeline, the same
seed. The only varied axis relative to EXP-004 is the pretraining
data; the only varied axis relative to EXP-007 is HAM10000 inclusion in
that pretraining data.

\subsection{Decision table}
Identical to Table~\ref{tab:exp009-decision} in \S\ref{sec:followup}.
Outcome bands partition $[0, 1]$ exhaustively so that no observed
outcome falls into an unmapped region:
\begin{itemize}
\item Test $\auroc \geq 0.85$: dermoscopy-domain transfer is sufficient
      under this scaffold. Headline survives; contamination caveat
      downgrades from ``unpartitioned'' to ``ruled out.''
\item Test $\auroc$ in $[0.80, 0.85)$: borderline transfer / near miss.
      Headline survives weakened, with the borderline explicitly
      acknowledged: ``dermoscopy-domain pretraining is a substantial but
      not full driver, and the contamination caveat is downgraded but
      not eliminated.''
\item Test $\auroc$ in $[0.50, 0.80)$: partial transfer; both factors
      contribute. Claim becomes ``dermoscopy-domain pretraining helps,
      HAM10000 image overlap helps more.''
\item Test $\auroc$ in $[0.30, 0.50)$: HAM10000 overlap drove EXP-007.
      Claim narrows to ``frozen-backbone JEPA unlocks when the backbone
      has seen the eval dataset, not when it has seen the eval
      domain.''
\item Test $\auroc < 0.30$: below-random inversion in the same regime
      as EXP-004 / EXP-006a / EXP-006b. Claim narrows further:
      ``dermoscopy-domain pretraining without the eval dataset behaves
      like natural-image pretraining under this scaffold,'' and the
      EXP-007 swing is then attributable specifically to HAM10000
      image-level overlap rather than to dermoscopy-domain pretraining
      in general. A pretrain-quality check (\S\ref{app:exp009-design}
      below) is required to rule out a weak self-pretrain as the
      cause before this band is acted on.
\end{itemize}

\subsection{Why we share the design before running it}
Three concrete costs would gate any launch:
\begin{enumerate}[label=(\arabic*), leftmargin=2em]
\item \emph{Provenance audit.} Confirming HAM10000 exclusion on every
      ISIC component requires a per-image hash check against the
      HAM10000 manifest --- the audit is straightforward but is itself
      a multi-day engineering task before any GPU is spent.
\item \emph{Pretrain compute.} DINOv2 ViT-B/14 pretraining on
      $\sim$$200{,}000$ steps requires a non-trivial GPU budget that is
      not in the free-tier envelope used for the other nine runs.
\item \emph{Pretrain-quality validation.} A weak pretraining run that
      never learns dermoscopy structure would produce a low test
      $\auroc$ that the decision table would mis-attribute to the
      lower bands when the actual cause is pretrain failure. A held-out
      diagnostic would be needed to disambiguate.
\end{enumerate}
We share the methodology and the nine-run arc at this stage to invite
feedback on the proxy-task design and on whether this partition is the
right next step. Whether to ultimately run EXP-009, modify it, or
pursue a different follow-up depends on that feedback.
